\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-05-06 manuscript/main.tex
Add files via upload

@@

To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market. Each type of brokerage follows a standard percentage charge by $r_j$ and they can not manipulate the percentage charge in each submarket.

@@

There are $L$ number of customers that arrive in the market at random poission rate $\lambda$ and for current issue, we can first assume that the customers are indifferent when selecting the brokerages and we can release this assumption later to make the customers have private preference towards each type of brokerages. The probability of selecting the brokerage $i$ is given by:

@@

The result presented in the table \ref{tab:entry_effect} examines the effect of a Lianjia's entry into an area on various outcomes. Prior to the Lianjia's entry ($pre_2$), there is no statistically significant effect on any of the three outcomes, suggesting that anticipation of the Lianjia's entry does not affect these metrics. In addition, there is a significant 4\% increase in revenue after the Lianjia's entry ($entry$), suggesting a substantial increase in Lianjia sales. However, the effect on price concessions and number of showings remains statistically insignificant, suggesting that Lianjia's entry does not lead to significant changes in pricing strategies or the number of showings brought to the area.

@@

We treat the 2016's sample as the base year, and other settings are consistent with previous table \ref{tab:Dynamic}. The result is reported in Figure \ref{fig:dynamic_effect}

>>>>

\emph{This should be based on the brokerages' network}

@@

This follows from \citep{Armstrong2006}.

Our model is in line with the real world setting that the sellers are hard to know about which platform can bring how many buyers to the market but the buyers can search all the information available online to decide which house they can assess.

To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market. Each type of brokerage follows a standard percentage charge by $r_j, j \in \{1, 2\}$ and they can not manipulate the percentage charge in each submarket.

@@

There are $L$ number of customers and we can first assume that the customers are indifferent when selecting the brokerages and we can release this assumption later to make the customers have private preference towards each type of brokerages. The probability of selecting the brokerage $i$ is given by:

@@

The result presented in the table \ref{tab:entry_effect} examines the effect of Lianjia's offline stores' entry into an area on various outcomes. Prior to the Lianjia's entry ($pre_2$), there is no statistically significant effect on any of the three outcomes, suggesting that anticipation of the Lianjia's entry does not affect these metrics. In addition, there is a significant 4\% increase in revenue after the Lianjia's entry ($entry$), suggesting a substantial increase in Lianjia sales. However, the effect on price concessions and number of showings remains statistically insignificant, suggesting that Lianjia's entry does not lead to significant changes in pricing strategies or the number of showings brought to the area.

@@

We treat the year 2016 as the base year, and other settings are consistent with previous table \ref{tab:Dynamic}. The result is reported in Figure \ref{fig:dynamic_effect}
